\section{Introduction}
The prevalence of Large Language Models (LLMs) in education has opened up new avenues for enhancing student learning and academic support. LLMs have the potential to analyze vast amounts of educational data, identify patterns, and provide personalized recommendations to students and educators alike. In this study, we focus on leveraging the capabilities of LLMs to analyze students examination results and identify the level of assistance they require to succeed academically. 

Using multiple prompting techniques, we analyze a given dataset of students' examination results, split into training and testing sets, to identify patterns and factors that contribute to academic success or failure in order to provide an appropriate level of academic support. We classify students' level of assistance required into different categories based on their performance, then instruct the LLMs to train themselves with the training sets and evaluate their performance on the testing sets. 

By identifying at-risk students early on, Higher Education Institutions (HEIs) can implement strategies to improve retention rates and enhance the overall educational experience; students can also benefit from the predictions provided by the LLMs as an early-warning system. The results of this study can inform policy decisions and contribute to the development of more effective support systems for students in HEIs.

In order to determine the scope of our work, we begin by utilizing the systematic literature review framework devised by \cite{KeathleyHerring2016}. To this end, section 2 and 3 will elaborate on models background and choice, data collection, and evaluation metrics. Section 4 and 5 will describe present the methodology and experimental setup, including data preprocessing, feature selection, and model training. Finally, Section 6 will discuss the results and implications of our findings, as well as potential future research directions in this area.